Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-07 manuscript.tex
6 updates

We measured the standard errors of each CCF parameters for all the CCFs of HD215152, HD192310 and Corot-7. This gives us an information of how the noise on each CCF parameter varies as a function of SNR. In this case, the SNR, measured at 550 nm on the original spectra, varies between 10 and 500. The results can be seen in Fig.~\ref{fig:se}. In the top plots of this figure, we show the standard errors for the different RV, width and asymmetry estimates. Note that because BIS SPAN and $\gamma$ does not have the same units, we used the slope of the correlation between those two parameters to transform $\gamma$ in \ms (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star). In the bottom plots, we show the ratio between the standard errors measured when using the SN parameters and the Normal parameters. Values smaller or larger than one will imply that standard errors from the SN parameters are more or less precise, respectively.

>>>>

The standard errors were also computed for each CCF parameter for all the CCFs of HD215152, HD192310 and Corot-7. 
This provides information on how the noise of each CCF parameter varies as a function of SNR, where the SNR measured at 550 nm on the original spectra varies between 10 and 500. 
The combined results for all the stars considered are displayed in Fig.~\ref{fig:se}. 
The top plots show the standard errors of the three different estimated RV's, the width, and the asymmetry estimates. 
Note that because BIS SPAN and $\gamma$ do not have the same units, the estimated slopes of the correlation between those two parameters to transform $\gamma$ in \ms were used (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star). 
In the bottom plots show the ratio between the standard errors measured when using the SN parameters and the Normal parameters. Values smaller or larger than one will imply that standard errors from the SN parameters are more or less precise than the Normal parameters, respectively.
